Accuracy in Parameter Estimation and Simulation Approaches for Sample Size Planning Accounting for Item Effects

### 2024-12-03 manuscript_draft.tex
updating disclosures

\begin{itemize}
\tightlist
\item
  Data: All data used in this manuscript and vignettes have been cited and can be found on our repository pages (\url{https://github.com/SemanticPriming/stimuli-power}).
\item
  Analysis Code:

  \begin{itemize}
  \tightlist
  \item
    Manuscript repository with code and data: \url{https://osf.io/swmva/} or \url{https://github.com/SemanticPriming/stimuli-power}
  \item
    Package repository with vignettes and data: \url{https://github.com/SemanticPriming/semanticprimeR}
  \end{itemize}
\item
  Pre-registration: We did not pre-register this study, as it was a simulation study.
\item
  Materials: No materials were used.
\item
  Funding: no funding was provided for this study.
\item
  Conflicts of interest: the researchers declare no conflicts of interest.
\end{itemize}

>>>>

\begin{itemize}
\tightlist
\item
  Funding: no funding was provided for this study.
\item
  Conflicts of interest: the researchers declare no conflicts of interest.
\item
  Ethics approval: not applicable, simulation study.
\item
  Consent to participate: not applicable, simulation study.
\item
  Consent for publication: all authors approved the manuscript, no participant approval necessary.
\item
  Data: All data used in this manuscript and vignettes have been cited and can be found on our repository pages (\url{https://github.com/SemanticPriming/stimuli-power}).
\item
  Materials: No materials were used.
\item
  Analysis Code:

  \begin{itemize}
  \tightlist
  \item
    Manuscript repository with code and data: \url{https://osf.io/swmva/} or \url{https://github.com/SemanticPriming/stimuli-power}
  \item
    Package repository with vignettes and data: \url{https://github.com/SemanticPriming/semanticprimeR}
  \end{itemize}
\item
  Pre-registration: We did not pre-register this study, as it was a simulation study.
\item
  Author contributions are printed at the top of the manuscript automatically in \emph{papaja}.
\end{itemize}
